---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(tidyverse)
```

# stat5730covid19

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

This is an rough and unpolished R data package for the students of STAT 5730.
It contains data COVID-19 data from the Johns Hopkins
CSSE group, The COVID Tracking Project, the New York Times, the state
executive orders shared Google sheet collected by the Spring 2020 STAT
5730 class, the Google Mobility Report, and other related data. 
The data will be updated regularly for now, so please reinstall the package 
to get new data.

Where possible, I have included FIPS codes for the geographic regions of the 
United States. This is a standardized code used by the U.S. federal government 
to identify states (with 2 digits) and counties (with 5 digits). In many cases, 
you can use the FIPS code as a key for joining tables.

Also included with the package are county- and state-level estimates of 
population, density, and median income from the U.S. Census Bureau for 2018. 
The `GEOID` variable in the data can be treated as a FIPS code.

## Installation

You can install stat5730covid19 from [Github](https://github.com) with:

``` r
remotes::install_github("vqv/stat5730covid19")
```

Note that you will need to have the 
[`remotes` package](https://github.com/r-lib/remotes) installed in order 
to use `remotes::install_github()`. 

## Examples

```{r example}
library(stat5730covid19)
```

### JHU CSSE

Source: [https://github.com/CSSEGISandData/COVID-19](https://github.com/CSSEGISandData/COVID-19)

The CSSE group at Johns Hopkins has been collecting data on the global 
COVID-19 pandemic. Their data includes number of cases and deaths in different 
regions globally.

```{r}
csse_global
```
```{r}
csse_us
```
```{r}
csse_lookup
```

### COVID Tracking Project

Source: [https://covidtracking.com](https://covidtracking.com)

The COVID Tracking Project was initiated by journalists at The Atlantic 
magazine. The data provides daily case and death counts at the state level, 
as well as numbers of tests and negative results, and hospital data.

```{r}
covidtracking
```

### New York Times

Source: [https://github.com/nytimes/covid-19-data](https://github.com/nytimes/covid-19-data)

Journalists and data scientists at the New York Times have been working on 
collecting daily case and death counts at the U.S. county level.

```{r}
nyt_county
```

### STAT 5730

The students of Spring 2020 STAT 5730 collected data on the executive orders 
made by U.S. state governments mandating school closures, shelter in place 
(stay at home), and travel restrictions.

```{r}
state_orders
```

### Google Mobility

Source: [https://www.google.com/covid19/mobility/index.html?hl=en](https://www.google.com/covid19/mobility/index.html?hl=en)

Google is temporarily providing estimates of mobility in different locations 
that are based on anonymized data collected from users who have enabled 
location history. The values are percent change from a baseline 
median value on the same day of the week during a 5 week period from the 
beginning of the year.

Notes from Google:

> Location accuracy and the understanding of categorized places varies from 
> region to region, so we don’t recommend using this data to compare changes 
> between countries, or between regions with different characteristics (e.g. 
> rural versus urban areas).

```{r}
google_mobility
```

### U.S. Census data

```{r}
census_state_pop
```
```{r}
census_county_pop
```
```{r}
census_county_income
```
